---
title: "food_cyclone2022"
author: "Andrianony Ny Aina Ianjatina"
date: "`r Sys.Date()`"
output: html_document
---

```{r, include=FALSE, echo=FALSE}
#load packages and library
library(tidyverse)    
library(haven)        
library(stringdist)
library(tictoc)
library(progressr)
library(future)
library(furrr)
library(gt)
library(readxl)
library(fs)
library(dplyr)
library(ggplot2)
library(fixest)
library(labelled)
library(expss)
library(haven)
```

```{r, include=FALSE, echo=FALSE}
#set working directory
setwd ("/Users/nyainaianjatinaandrianony/Desktop/food_insecurity_cyclone_Madagascar/food_cyclone_2022")
```

First, load data for food insecurity

```{r}
fs20 <- read_dta ("raw_data/HPS2020/S08_SECU.dta")
fs21 <- read_dta ("raw_data/HPS2021/S08_SECU.dta")
fs22 <- read_dta ("raw_data/HPS2022/S08_SECU.dta")
fs23 <- read_dta ("raw_data/HPS2023/S08_SECU.dta")
```

```{r}
fs <- bind_rows(fs20, fs21, fs22, fs23)
```

create treatment variable

```{r}
# Define district lists for cyclones
cyclone1_districts <- c(
  "ANTANANARIVO_RENIVOHITRA", "AMBALAVAO", "AMBATOFINANDRAHANA", "AMBATOLAMPY", "AMBOASARY",
  "AMBOHIDRATRIMO", "AMBOHIMAHASOA", "AMBOSITRA", "AMBOVOMBE", "AMPANIHY", "ANDRAMASINA",
  "ANKAZOABO", "ANOSIBE_AN_ALA", "ANTANAMBAO_MANAMPOTSY", "ANTANANARIVO_ATSIMONDRANO",
  "ANTANANARIVO_AVARADRANO", "ANTANIFOTSY", "ANTSIRABEI", "ANTSIRABEII", "ARIVONIMAMO", 
  "BEFOTAKA", "BEKILY", "BELOHA", "BENENITRA", "BEROROHA", "BETAFO", "BETIOKY-SUD", 
  "BETROKA", "BRICKAVILLE", "FANDRIANA", "FARAFANGANA", "FARATSIHO", "FIANARANTSOA", 
  "IAKORA", "ISANDRA", "IVOHIBE", "LALANGINA", "MAHABO", "MAHANORO", "MANAKARA", 
  "MANANDRIANA", "MANANJARY", "MANDOTO", "MANJA", "MANJAKANDRIANA", "MAROLAMBO", 
  "MIDONGY", "MORAMANGA", "MOROMBE", "MORONDAVA", "NOSY VARIKA", "SAKARAHA", 
  "SOAVINANDRIANA", "TAOLAGNARO", "TULEAR-I", "TULEAR-II", "TSIHOMBE", "VANGAINDRANO", 
  "VATOMANDRY", "VOHIBATO", "VOHIPENO", "VONDROZO", "IFANADIANA", "IHOSY", "IKALAMAVONY", 
  "IKONGO"
)

cyclone2_districts <- c(
  "AMBALAVAO", "AMBATOFINANDRAHANA", "AMBOHIMAHASOA", "AMBOSITRA", "ANKAZOABO", 
  "ANOSIBE_AN_ALA", "ANTANAMBAO_MANAMPOTSY", "ANTANIFOTSY", "ANTSIRABEI", "ANTSIRABEII", 
  "BENENITRA", "BEROROHA", "IFANADIANA", "BETAFO", "BETIOKY-SUD", "FANDRIANA", 
  "FIANARANTSOA", "IHOSY", "IKALAMAVONY", "IKONGO", "ISANDRA", "IVOHIBE", "LALANGINA", 
  "MAHABO", "MAHANORO", "MANAKARA", "MANANDRIANA", "MANANJARY", "MANJA", "MAROLAMBO", 
  "MOROMBE", "MORONDAVA", "NOSY VARIKA", "SAKARAHA", "TULEAR-I", "TULEAR-II", 
  "VOHIBATO", "VOHIPENO", "VONDROZO"
)

# Create variables cyclone1 and cyclone2
fs$cyclone1 <- ifelse(fs$district %in% cyclone1_districts, 1, 0)
fs$cyclone2 <- ifelse(fs$district %in% cyclone2_districts, 1, 0)

# Create treatment variable
fs$treatment <- ifelse(fs$cyclone1 == 1 & fs$cyclone2 == 0, 1, 
                       ifelse(fs$cyclone1 == 1 & fs$cyclone2 == 1, 2, 0))
fs <- fs %>%
  mutate(both_cyclone = ifelse(cyclone1 == 1 & cyclone2 == 1, 1, 0))
fs <- fs %>%
  mutate(cyclone_control = ifelse(treatment == 0, 1, 0))
#create a variable post_2022
fs <- fs %>%
  mutate(post_2022 = if_else(year >= 2022, 1, 0))  # 1 for post-2022, 0 for before
```

Create food consumption score (fcs)

```{r}
# Label relevant FCS variables ------------------------------------------------# 
var_label(fs$q8b_03_1)   <- "Consumption over the past 7 days: cereals, grains and tubers"
var_label(fs$q8b_03_2)  <- "Consumption over the past 7 days: pulses"
var_label(fs$q8b_03_6)  <- "Consumption over the past 7 days: dairy products"
var_label(fs$q8b_03_4)     <- "Consumption over the past 7 days: meat, fish and eggs"
var_label(fs$q8b_03_3)    <- "Consumption over the past 7 days: vegetables"
var_label(fs$q8b_03_5)  <- "Consumption over the past 7 days: fruit"
var_label(fs$q8b_03_7)    <- "Consumption over the past 7 days: fat and oil"
var_label(fs$q8b_03_8)  <- "Consumption over the past 7 days: sugar or sweets:"
var_label(fs$q8b_03_9)   <- "Consumption over the past 7 days: condiments or spices"
```

```{r}
# rename the variables
fs <- fs %>%
  rename(
    FCSStap = q8b_03_1,
    FCSPulse = q8b_03_2,
    FCSDairy = q8b_03_6,
    FCSPr = q8b_03_4,
    FCSVeg = q8b_03_3,
    FCSFruit = q8b_03_5,
    FCSFat = q8b_03_7,
    FCSSugar = q8b_03_8,
    FCSCond = q8b_03_9
  )
```

```{r}
#calculate FCS
fs <- fs %>% mutate(FCS = (2 * FCSStap) + (3 * FCSPulse)+ (4*FCSPr) +FCSVeg  +FCSFruit +(4*FCSDairy) + (0.5*FCSFat) + (0.5*FCSSugar))
#create FCG groups based on 21/25 or 28/42 thresholds
fs <- fs %>% mutate(
  FCSCat21 = case_when(
    FCS <= 21 ~ "Poor", between(FCS, 21.5, 35) ~ "Borderline", FCS > 35 ~ "Acceptable"),
  FCSCat28 = case_when(
    FCS <= 28 ~ "Poor", between(FCS, 28.5, 42) ~ "Borderline", FCS > 42 ~ "Acceptable"))
var_label(fs$FCSCat21) <- "Food Consumption Group 21/35 thresholds"
var_label(fs$FCSCat28) <-  "Food Consumption Group 28/42 thresholds"
```


```{r}
#rename some variables
fs <- fs %>%
  rename(male = q1_01 , marital_status = q1_07)
fs <- fs %>%
  rename(rural = milieu) %>%
  mutate(rural = ifelse(rural == 0, 1, 0)) 
```

Calculate Food Insecurity Experience Scale (FIES)

```{r}
# Function to calculate FIES score based on binary responses (1 or 0)
calculate_fies <- function(fs) {
  # Define the column names for the 8 questions
  required_columns <- c("q8a_01a", "q8a_02a", "q8a_03a", "q8a_04a", 
                        "q8a_05a", "q8a_06a", "q8a_07a", "q8a_08a")
  
  # Check that all required columns exist in the data
  if(all(required_columns %in% colnames(fs))) {
    # Calculate the FIES score by summing the binary responses (0 or 1)
    fs$FIES_score <- rowSums(fs[, required_columns], na.rm = TRUE)
  } else {
    stop("Data does not contain all the required columns (q8a_01a to q8a_08a).")
  }
  return(fs)
}

# Apply the function to calculate the FIES score
fs <- calculate_fies(fs)
```

add education data
```{r}
educ20 <- read_dta("raw_data/HPS2020/S02_EDUC.dta")
educ21 <- read_dta("raw_data/HPS2021/S02_EDUC.dta")
educ22 <- read_dta("raw_data/HPS2022/S02_EDUC.dta")
educ23 <- read_dta("raw_data/HPS2023/S02_EDUC.dta")
```

```{r}
#create year variable
educ20$year <- 2020
educ21$year <- 2021
educ22$year <- 2022
educ23$year <- 2023
```

```{r}
educ<- bind_rows(educ20, educ21, educ22, educ23)
```

```{r}
educ<- educ %>%
  distinct(hhgrap, hhnum, year, .keep_all = TRUE)
df <- left_join(fs, educ, by = c("hhgrap", "hhnum","year"))
```

```{r}
#rename some variables
df <- df %>%
  rename(educ = q2_26)
```

add occupation data
```{r}
ocup20 <- read_dta("raw_data/HPS2020/S04_EMPL_AL.dta")
ocup21 <- read_dta("raw_data/HPS2021/S04_EMPL_AL.dta")
ocup22 <- read_dta("raw_data/HPS2022/S04_EMPL_AI.dta")
ocup23 <- read_dta("raw_data/HPS2023/S04_EMPL_AL.dta")
```

```{r}
#create year variable
ocup20$year <- 2020
ocup21$year <- 2021
ocup22$year <- 2022
ocup23$year <- 2023
```

```{r}
ocup<- bind_rows(ocup20, ocup21, ocup22, ocup23)
```

```{r}
ocup<- ocup %>%
  distinct(hhgrap, hhnum, year, .keep_all = TRUE)
df <- left_join(df, ocup, by = c("hhgrap", "hhnum","year"))
```

```{r}
#rename some variables
df <- df %>%
  rename(revenu = q4a_46a)
```

We need now to work on some mechanism
1. Food production

```{r}
agri20 <- read_dta("raw_data/HPS2020/S16_AGRI.dta")
agri21 <- read_dta("raw_data/HPS2021/S16_AGRI.dta")
agri22 <- read_dta("raw_data/HPS2022/S16_AGRI.dta")
agri23 <- read_dta("raw_data/HPS2023/S16_AGRI.dta")
```

cleaning data for 2020
```{r, include=FALSE, echo=FALSE}
agri20 <- agri20 %>%
  mutate(food_production = q16c_12 + q16c_12a)

agri20 <- agri20 %>%
  mutate(price = q16c_17/q16c_16)

price <- agri20 %>%
  group_by(q16c_05, price) %>%
  summarise(values = paste(unique(q16c_16_uml), collapse = ", "), .groups = "drop") %>%
  arrange(q16c_05, price)
price <- price %>% rename(food_item = q16c_05, 
                      prix = price)
price_unique <- price %>%
  distinct(food_item, values, .keep_all = TRUE) %>%
  group_by(food_item, values) %>%
  summarize(price_mean = mean(prix, na.rm = TRUE), .groups = "drop")
# calculate household food production
agri20 <- agri20 %>%
  mutate(q16c_12a_uml = as.numeric(q16c_12a_uml)) %>%
  left_join(price_unique %>% mutate(values = as.numeric(values)), 
            by = c("q16c_05" = "food_item", "q16c_12a_uml" = "values")) %>%
  mutate(price12 = price_mean)

agri20 <- agri20 %>%
  mutate(production = food_production*price12)
# calculate household auto-food cons
agri20 <- agri20 %>%
  mutate(q16c_13_uml = as.numeric(q16c_13_uml)) %>%
  left_join(price_unique %>%
              mutate(values = as.numeric(values)), 
            by = c("q16c_05" = "food_item", "q16c_13_uml" = "values"))
agri20 <- agri20 %>% rename(price13 = price_mean.y) 
agri20 <- agri20 %>%
  mutate(autocons = q16c_13*price13)
# calculate household gift-food
agri20 <- agri20 %>%
  mutate(q16c_14_uml = as.numeric(q16c_14_uml)) %>%
  left_join(price_unique %>%
              mutate(values = as.numeric(values)), 
            by = c("q16c_05" = "food_item", "q16c_14_uml" = "values"))
agri20 <- agri20 %>% rename(price14 = price_mean) 
agri20 <- agri20 %>%
  mutate(gift_food = q16c_14*price14)
#food production
agri201 <- agri20 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_food_production = sum(as.numeric(production), na.rm = TRUE), 
  ) %>%
  ungroup() 
agri202 <- agri20 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(agri201, by = c("hhgrap", "hhnum")) 
#household autocons
agri203 <- agri20 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_autocons = sum(as.numeric(autocons), na.rm = TRUE), 
  ) %>%
  ungroup() 
agri205 <- left_join(agri202, agri203, by = c("hhgrap", "hhnum"))
#gift food
agri206 <- agri20 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_gift_food = sum(as.numeric(gift_food), na.rm = TRUE), 
  ) %>%
  ungroup() 
agri207 <- left_join(agri205, agri206, by = c("hhgrap", "hhnum"))
#sales
agri208 <- agri20 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_sales = sum(as.numeric(q16c_17), na.rm = TRUE), 
  ) %>%
  ungroup() 
agri209 <- left_join(agri207, agri208, by = c("hhgrap", "hhnum"))
```

cleaning data for 2021

```{r, include=FALSE, echo=FALSE}
agri21 <- agri21 %>%
  mutate(food_production = q16c_12+q16c_12a)
agri21 <- agri21 %>%
  mutate(price = q16c_17/q16c_16)
price <- agri21 %>%
  group_by(q16c_05, price) %>%
  summarise(values = paste(unique(q16c_16_uml), collapse = ", "), .groups = "drop") %>%
  arrange(q16c_05, price)
#rename variables
price <- price %>% rename(food_item = q16c_05, 
                      prix = price)
price_unique <- price %>%
  distinct(food_item, values, .keep_all = TRUE) %>%
  group_by(food_item, values) %>%
  summarize(price_mean = mean(prix, na.rm = TRUE), .groups = "drop")
# calculate household food production
agri21 <- agri21 %>%
  mutate(q16c_12a_uml = as.numeric(q16c_12a_uml)) %>%
  left_join(price_unique %>% mutate(values = as.numeric(values)), 
            by = c("q16c_05" = "food_item", "q16c_12a_uml" = "values")) %>%
  mutate(price12 = price_mean)

agri21 <- agri21 %>%
  mutate(production = food_production*price12)
# calculate household auto-food cons
agri21 <- agri21 %>%
  mutate(q16c_13_uml = as.numeric(q16c_13_uml)) %>%
  left_join(price_unique %>%
              mutate(values = as.numeric(values)), 
            by = c("q16c_05" = "food_item", "q16c_13_uml" = "values"))
agri21 <- agri21 %>% rename(price13 = price_mean.y) 
agri21 <- agri21 %>%
  mutate(autocons = q16c_13*price13)

# calculate household gift-food
agri21 <- agri21 %>%
  mutate(q16c_14_uml = as.numeric(q16c_14_uml)) %>%
  left_join(price_unique %>%
              mutate(values = as.numeric(values)), 
            by = c("q16c_05" = "food_item", "q16c_14_uml" = "values"))
agri21 <- agri21 %>% rename(price14 = price_mean) 
agri21 <- agri21 %>%
  mutate(gift_food = q16c_14*price14)
#food production
agri211 <- agri21 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_food_production = sum(as.numeric(production), na.rm = TRUE), 
  ) %>%
  ungroup() 
agri212 <- agri21 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(agri201, by = c("hhgrap", "hhnum")) 
#household autocons
agri213 <- agri21 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_autocons = sum(as.numeric(autocons), na.rm = TRUE), 
  ) %>%
  ungroup() 
agri215 <- left_join(agri212, agri213, by = c("hhgrap", "hhnum"))
#gift food
agri216 <- agri21 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_gift_food = sum(as.numeric(gift_food), na.rm = TRUE), 
  ) %>%
  ungroup() 
agri217 <- left_join(agri215, agri216, by = c("hhgrap", "hhnum"))
#sales
agri218 <- agri21 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_sales = sum(as.numeric(q16c_17), na.rm = TRUE), 
  ) %>%
  ungroup() 
agri219 <- left_join(agri217, agri218, by = c("hhgrap", "hhnum"))
```

cleaning data for 2022
```{r, include=FALSE, echo=FALSE}
agri22 <- agri22 %>%
  mutate(food_production = q16c_12+q16c_12a)
agri22 <- agri22 %>%
  mutate(price = q16c_17/q16c_16)
price <- agri22 %>%
  group_by(q16c_05, price) %>%
  summarise(values = paste(unique(q16c_16_uml), collapse = ", "), .groups = "drop") %>%
  arrange(q16c_05, price)
#rename variables
price <- price %>% rename(food_item = q16c_05, 
                      prix = price)
price_unique <- price %>%
  distinct(food_item, values, .keep_all = TRUE) %>%
  group_by(food_item, values) %>%
  summarize(price_mean = mean(prix, na.rm = TRUE), .groups = "drop")
# calculate household food production
price_unique_clean <- price_unique %>%
  mutate(values = as.numeric(values)) %>%
  distinct(food_item, values, .keep_all = TRUE)

agri22 <- agri22 %>%
  mutate(q16c_12a_uml = as.numeric(q16c_12a_uml)) %>%
  left_join(price_unique_clean, 
            by = c("q16c_05" = "food_item", "q16c_12a_uml" = "values")) %>%
  mutate(price12 = price_mean)
agri22 <- agri22 %>%
  mutate(production = food_production*price12)
# calculate household auto-food cons
price_unique_clean <- price_unique %>%
  mutate(values = as.numeric(values)) %>%
  distinct(food_item, values, .keep_all = TRUE)

agri22 <- agri22 %>%
  mutate(q16c_13_uml = as.numeric(q16c_13_uml)) %>%
  left_join(price_unique_clean, 
            by = c("q16c_05" = "food_item", "q16c_13_uml" = "values")) %>%
  mutate(price13 = price_mean.y)
agri22 <- agri22 %>%
  mutate(autocons = q16c_13*price12)

# calculate household gift-food
price_unique_clean <- price_unique %>%
  mutate(values = as.numeric(values)) %>%
  distinct(food_item, values, .keep_all = TRUE)
agri22 <- agri22 %>%
  mutate(q16c_14_uml = as.numeric(q16c_14_uml)) %>%
  left_join(price_unique_clean, 
            by = c("q16c_05" = "food_item", "q16c_13_uml" = "values")) %>%
  mutate(price14 = price_mean)
agri22 <- agri22 %>%
  mutate(gift_food = q16c_14*price12)
#food production
agri221 <- agri22 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_food_production = sum(as.numeric(production), na.rm = TRUE), 
  ) %>%
  ungroup() 
agri222 <- agri22 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(agri221, by = c("hhgrap", "hhnum")) 
#household autocons
agri223 <- agri22 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_autocons = sum(as.numeric(autocons), na.rm = TRUE), 
  ) %>%
  ungroup() 
agri225 <- left_join(agri222, agri223, by = c("hhgrap", "hhnum"))
#gift food
agri226 <- agri22 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_gift_food = sum(as.numeric(gift_food), na.rm = TRUE), 
  ) %>%
  ungroup() 
agri227 <- left_join(agri225, agri226, by = c("hhgrap", "hhnum"))
#sales
agri228 <- agri22 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_sales = sum(as.numeric(q16c_17), na.rm = TRUE), 
  ) %>%
  ungroup() 
agri229 <- left_join(agri227, agri228, by = c("hhgrap", "hhnum"))
```

cleaning data for 2023
```{r, include=FALSE, echo=FALSE}
agri23 <- agri23 %>%
  mutate(food_production = q16c_12+q16c_12a)
agri23 <- agri23 %>%
  mutate(price = q16c_17/q16c_16)
price <- agri23 %>%
  group_by(q16c_05, price) %>%
  summarise(values = paste(unique(q16c_16_uml), collapse = ", "), .groups = "drop") %>%
  arrange(q16c_05, price)
#rename variables
price <- price %>% rename(food_item = q16c_05, 
                      prix = price)
price_unique <- price %>%
  distinct(food_item, values, .keep_all = TRUE) %>%
  group_by(food_item, values) %>%
  summarize(price_mean = mean(prix, na.rm = TRUE), .groups = "drop")
# calculate household food production
agri23 <- agri23 %>%
  mutate(q16c_12a_uml = as.numeric(q16c_12a_uml)) %>%
  left_join(price_unique %>% mutate(values = as.numeric(values)), 
            by = c("q16c_05" = "food_item", "q16c_12a_uml" = "values")) %>%
  mutate(price12 = price_mean)

agri23 <- agri23 %>%
  mutate(production = food_production*price12)
# calculate household auto-food cons
agri23 <- agri23 %>%
  mutate(q16c_13_uml = as.numeric(q16c_13_uml)) %>%
  left_join(price_unique %>%
              mutate(values = as.numeric(values)), 
            by = c("q16c_05" = "food_item", "q16c_13_uml" = "values"))
agri23 <- agri23 %>% rename(price13 = price_mean.y) 
agri23 <- agri23 %>%
  mutate(autocons = q16c_13*price13)
# calculate household gift-food
agri23 <- agri23 %>%
  mutate(q16c_14_uml = as.numeric(q16c_14_uml)) %>%
  left_join(price_unique %>%
              mutate(values = as.numeric(values)), 
            by = c("q16c_05" = "food_item", "q16c_14_uml" = "values"))
agri23 <- agri23 %>% rename(price14 = price_mean) 
agri23 <- agri23 %>%
  mutate(gift_food = q16c_14*price14)
#food production
agri231 <- agri23 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_food_production = sum(as.numeric(production), na.rm = TRUE), 
  ) %>%
  ungroup() 
agri232 <- agri23 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(agri231, by = c("hhgrap", "hhnum")) 
#household autocons
agri233 <- agri23 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_autocons = sum(as.numeric(autocons), na.rm = TRUE), 
  ) %>%
  ungroup() 
agri235 <- left_join(agri232, agri233, by = c("hhgrap", "hhnum"))
#gift food
agri236 <- agri23 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_gift_food = sum(as.numeric(gift_food), na.rm = TRUE), 
  ) %>%
  ungroup() 
agri237 <- left_join(agri235, agri236, by = c("hhgrap", "hhnum"))
#sales
agri238 <- agri23 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_sales = sum(as.numeric(q16c_17), na.rm = TRUE), 
  ) %>%
  ungroup() 
agri239 <- left_join(agri237, agri238, by = c("hhgrap", "hhnum"))
```

```{r}
#create year variable
agri209$year <- 2020
agri219$year <- 2021
agri229$year <- 2022
agri239$year <- 2023
```

```{r}
agri <- bind_rows(agri209, agri219, agri229, agri239)
```

```{r}
agri <- agri %>%
  distinct(hhgrap, hhnum, year, .keep_all = TRUE)
df <- left_join(df, agri, by = c("hhgrap", "hhnum","year"))
```

```{r}
#rename some variables
df <- df %>%
  rename(culture_system = q16c_07, area_occupied = q16c_08, fertilizer_type = q16c_09)
```

add some more agriculture variable

```{r}
agria20 <- read_dta("raw_data/HPS2020/S16_AGRI_A.dta")
agria21 <- read_dta("raw_data/HPS2021/S16_AGRI_A.dta")
agria22 <- read_dta("raw_data/HPS2022/S16_AGRI_A.dta")
agria23 <- read_dta("raw_data/HPS2023/S16_AGRI_A.dta")
```

```{r}
#create year variable
agria20$year <- 2020
agria21$year <- 2021
agria22$year <- 2022
agria23$year <- 2023
```

```{r}
agria <- bind_rows(agria20, agria21, agria22, agria23)
```

```{r}
agria <- agria %>%
  distinct(hhgrap, hhnum, year, .keep_all = TRUE)
df <- left_join(df, agria, by = c("hhgrap", "hhnum","year"))
```

```{r}
#rename some variables
df <- df %>%
  rename(area_cultivated = q16a_09_n1)
df <- df %>%
  rename(fertility = q16a_20)
```

```{r}
agrib20 <- read_dta("raw_data/HPS2020/S16_AGRI_B.dta")
agrib21 <- read_dta("raw_data/HPS2021/S16_AGRI_B.dta")
agrib22 <- read_dta("raw_data/HPS2022/S16_AGRI_B.dta")
agrib23 <- read_dta("raw_data/HPS2023/S16_AGRI_B.dta")
```

```{r, include=FALSE, echo=FALSE}
agrib201 <- agrib20 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_intrants = sum(as.numeric(q16b_02), na.rm = TRUE), 
  ) %>%
  ungroup() 
agrib202 <- agrib20 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(agrib201, by = c("hhgrap", "hhnum")) 
agrib211 <- agrib21 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_intrants = sum(as.numeric(q16b_02), na.rm = TRUE), 
  ) %>%
  ungroup() 
agrib212 <- agrib21 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(agrib211, by = c("hhgrap", "hhnum")) 
agrib221 <- agrib22 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_intrants = sum(as.numeric(q16b_02), na.rm = TRUE), 
  ) %>%
  ungroup() 
agrib222 <- agrib22 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(agrib221, by = c("hhgrap", "hhnum")) 
agrib231 <- agrib23 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_intrants = sum(as.numeric(q16b_02), na.rm = TRUE), 
  ) %>%
  ungroup() 
agrib232 <- agrib23 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(agrib231, by = c("hhgrap", "hhnum")) 
```

```{r}
#create year variable
agrib202$year <- 2020
agrib212$year <- 2021
agrib222$year <- 2022
agrib232$year <- 2023
```

```{r}
agrib <- bind_rows(agrib202, agrib212, agrib222, agrib232)
```

```{r}
agrib <- agrib %>%
  distinct(hhgrap, hhnum, year, .keep_all = TRUE)
df <- left_join(df, agrib, by = c("hhgrap", "hhnum","year"))
```

add agricultural equipement variable

```{r}
equi20 <- read_dta("raw_data/HPS2020/S19_EQUI.dta")
equi21 <- read_dta("raw_data/HPS2021/S19_EQUI.dta")
equi22 <- read_dta("raw_data/HPS2022/S19_EQUI.dta")
equi23 <- read_dta("raw_data/HPS2023/S19_EQUI.dta")
```

```{r, include=FALSE, echo=FALSE}
equi201 <- equi20 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_equi = sum(as.numeric(q19_04), na.rm = TRUE), 
  ) %>%
  ungroup() 
equi202 <- equi20 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(equi201, by = c("hhgrap", "hhnum")) 
equi211 <- equi21 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_equi = sum(as.numeric(q19_04), na.rm = TRUE), 
  ) %>%
  ungroup() 
equi212 <- equi21 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(equi211, by = c("hhgrap", "hhnum")) 
equi221 <- equi22 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_equi = sum(as.numeric(q19_04), na.rm = TRUE), 
  ) %>%
  ungroup() 
equi222 <- equi22 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(equi221, by = c("hhgrap", "hhnum")) 
equi231 <- equi23 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_equi = sum(as.numeric(q19_04), na.rm = TRUE), 
  ) %>%
  ungroup() 
equi232 <- equi23 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(equi231, by = c("hhgrap", "hhnum")) 
```

```{r}
#create year variable
equi202$year <- 2020
equi212$year <- 2021
equi222$year <- 2022
equi232$year <- 2023
```

```{r}
equi <- bind_rows(equi202, equi212, equi222, equi232)
```

```{r}
equi <- equi %>%
  distinct(hhgrap, hhnum, year, .keep_all = TRUE)
df <- left_join(df, equi, by = c("hhgrap", "hhnum","year"))
```

Now, another mechanism is on household expenditure

Another indicator of food security would be food expenses

```{r}
exp20 <- read_dta("raw_data/HPS2020/S07_CONS_AL.dta")
exp21 <- read_dta("raw_data/HPS2021/S07_CONS_AL.dta")
exp22 <- read_dta("raw_data/HPS2022/S07_CONS_AL.dta")
exp23 <- read_dta("raw_data/HPS2023/S07_CONS_AL.dta")
```

create a district variable

```{r, include=FALSE, echo=FALSE}
exp201 <- exp20 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_exp = sum(as.numeric(q7b_08), na.rm = TRUE), 
  ) %>%
  ungroup() 
exp202 <- exp20 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(exp201, by = c("hhgrap", "hhnum")) 
exp211 <- exp21 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_exp = sum(as.numeric(q7b_08), na.rm = TRUE), 
  ) %>%
  ungroup() 
exp212 <- exp21 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(exp211, by = c("hhgrap", "hhnum")) 
exp221 <- exp22 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_exp = sum(as.numeric(q7b_08), na.rm = TRUE), 
  ) %>%
  ungroup() 
exp222 <- exp22 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(exp221, by = c("hhgrap", "hhnum")) 
exp231 <- exp23 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_exp = sum(as.numeric(q7b_08), na.rm = TRUE), 
  ) %>%
  ungroup() 
exp232 <- exp23 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(exp231, by = c("hhgrap", "hhnum")) 
```

```{r}
#create year variable
exp202$year <- 2020
exp212$year <- 2021
exp222$year <- 2022
exp232$year <- 2023
```

```{r}
exp <- bind_rows(exp202, exp212, exp222, exp232)
```

```{r}
exp <- exp %>%
  distinct(hhgrap, hhnum, year, .keep_all = TRUE)
df <- left_join(df, exp, by = c("hhgrap", "hhnum","year"))
```


another mechanism will be by decrease in non_food production

```{r}
nf20 <- read_dta("raw_data/HPS2020/S09_CONS.dta")
nf21 <- read_dta("raw_data/HPS2021/S09_CONS.dta")
nf22 <- read_dta("raw_data/HPS2022/S09_CONS.dta")
nf23 <- read_dta("raw_data/HPS2023/S09_CONS.dta")
```

```{r, include=FALSE, echo=FALSE}
nf201 <- nf20 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_nf = sum(as.numeric(q9b_03), na.rm = TRUE), 
  ) %>%
  ungroup() 
nf202 <- nf20 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(nf201, by = c("hhgrap", "hhnum")) 
nf211 <- nf21 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_nf = sum(as.numeric(q9b_03), na.rm = TRUE), 
  ) %>%
  ungroup() 
nf212 <- nf21 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(nf211, by = c("hhgrap", "hhnum")) 
nf221 <- nf22 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_nf = sum(as.numeric(q9b_03), na.rm = TRUE), 
  ) %>%
  ungroup() 
nf222 <- nf22 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(nf221, by = c("hhgrap", "hhnum")) 
nf231 <- nf23 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_nf = sum(as.numeric(q9b_03), na.rm = TRUE), 
  ) %>%
  ungroup() 
nf232 <- nf23 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(nf231, by = c("hhgrap", "hhnum")) 
```

```{r}
#create year variable
nf202$year <- 2020
nf212$year <- 2021
nf222$year <- 2022
nf232$year <- 2023
```

```{r}
nf <- bind_rows(nf202, nf212, nf222, nf232)
```

```{r}
nf <- nf %>%
  distinct(hhgrap, hhnum, year, .keep_all = TRUE)
df <- left_join(df, nf, by = c("hhgrap", "hhnum","year"))
```


```{r}
feols(log(sum_nf) ~ cyclone1 + both_cyclone + post_2022 + factor(treatment):post_2022| district + year, 
      data = nf,
      cluster = ~district)
```
another mechanism is on transfer
1. incoming transfer
```{r}
inctrans20 <- read_dta("raw_data/HPS2020/S13_TRAN_B1.dta")
inctrans21 <- read_dta("raw_data/HPS2021/S13_TRAN_B1.dta")
inctrans22 <- read_dta("raw_data/HPS2022/S13_TRAN_B1.dta")
inctrans23 <- read_dta("raw_data/HPS2023/S13_TRAN_B1.dta")
```


```{r, include=FALSE, echo=FALSE}
inctrans201 <- inctrans20 %>%
  group_by(hhgrap, hhnum) %>%
  summarize(
    sum1_inctrans = sum(as.numeric(q13_18a), na.rm = TRUE),
    sum2_inctrans = sum(as.numeric(q13_21a), na.rm = TRUE)
  ) %>%
  ungroup()
inctrans201 <- inctrans201 %>%
  mutate(sum_inctrans = as.numeric(sum1_inctrans) + as.numeric(sum2_inctrans))
inctrans202 <- inctrans20 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(inctrans201, by = c("hhgrap", "hhnum")) 
inctrans211 <- inctrans21 %>%
  group_by(hhgrap, hhnum) %>%
  summarize(
    sum1_inctrans = sum(as.numeric(q13_18a), na.rm = TRUE),
    sum2_inctrans = sum(as.numeric(q13_21a), na.rm = TRUE)
  ) %>%
  ungroup()
inctrans211 <- inctrans211 %>%
  mutate(sum_inctrans = as.numeric(sum1_inctrans) + as.numeric(sum2_inctrans))
inctrans212 <- inctrans21 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(inctrans211, by = c("hhgrap", "hhnum")) 
inctrans221 <- inctrans22 %>%
  group_by(hhgrap, hhnum) %>%
  summarize(
    sum1_inctrans = sum(as.numeric(q13_18a), na.rm = TRUE),
    sum2_inctrans = sum(as.numeric(q13_21a), na.rm = TRUE)
  ) %>%
  ungroup()
inctrans221 <- inctrans221 %>%
  mutate(sum_inctrans = as.numeric(sum1_inctrans) + as.numeric(sum2_inctrans))
inctrans222 <- inctrans22 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(inctrans221, by = c("hhgrap", "hhnum")) 
inctrans231 <- inctrans23 %>%
  group_by(hhgrap, hhnum) %>%
  summarize(
    sum1_inctrans = sum(as.numeric(q13_18a), na.rm = TRUE),
    sum2_inctrans = sum(as.numeric(q13_21a), na.rm = TRUE)
  ) %>%
  ungroup()
inctrans231 <- inctrans231 %>%
  mutate(sum_inctrans = as.numeric(sum1_inctrans) + as.numeric(sum2_inctrans))
inctrans232 <- inctrans23 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(inctrans231, by = c("hhgrap", "hhnum")) 
```

```{r}
#create year variable
inctrans202$year <- 2020
inctrans212$year <- 2021
inctrans222$year <- 2022
inctrans232$year <- 2023
```


```{r}
inctrans <- bind_rows(inctrans202, inctrans212, inctrans222, inctrans232)
```

```{r}
inctrans <- inctrans %>%
  distinct(hhgrap, hhnum, year, .keep_all = TRUE)
df <- left_join(df, inctrans, by = c("hhgrap", "hhnum","year"))
```

2. mechanism on outgoing transfer
```{r}
outtrans20 <- read_dta("raw_data/HPS2020/S13_TRAN_B2.dta")
outtrans21 <- read_dta("raw_data/HPS2021/S13_TRAN_B2.dta")
outtrans22 <- read_dta("raw_data/HPS2022/S13_TRAN_B2.dta")
outtrans23 <- read_dta("raw_data/HPS2023/S13_TRAN_B2.dta")
```

```{r, include=FALSE, echo=FALSE}
outtrans201 <- outtrans20 %>%
  group_by(hhgrap, hhnum) %>%
  summarize(
    sum1_outtrans = sum(as.numeric(q13_39a), na.rm = TRUE),
    sum2_outtrans = sum(as.numeric(q13_42a), na.rm = TRUE)
  ) %>%
  ungroup()
outtrans201 <- outtrans201 %>%
  mutate(sum_outtrans = as.numeric(sum1_outtrans) + as.numeric(sum2_outtrans))
outtrans202 <- outtrans20 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(outtrans201, by = c("hhgrap", "hhnum")) 
outtrans211 <- outtrans21 %>%
  group_by(hhgrap, hhnum) %>%
  summarize(
    sum1_outtrans = sum(as.numeric(q13_39a), na.rm = TRUE),
    sum2_outtrans = sum(as.numeric(q13_42a), na.rm = TRUE)
  ) %>%
  ungroup()
outtrans211 <- outtrans211 %>%
  mutate(sum_outtrans = as.numeric(sum1_outtrans) + as.numeric(sum2_outtrans))
outtrans212 <- outtrans21 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(outtrans211, by = c("hhgrap", "hhnum")) 
outtrans221 <- outtrans22 %>%
  group_by(hhgrap, hhnum) %>%
  summarize(
    sum1_outtrans = sum(as.numeric(q13_39a), na.rm = TRUE),
    sum2_outtrans = sum(as.numeric(q13_42a), na.rm = TRUE)
  ) %>%
  ungroup()
outtrans221 <- outtrans221 %>%
  mutate(sum_outtrans = as.numeric(sum1_outtrans) + as.numeric(sum2_outtrans))
outtrans222 <- outtrans22 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(outtrans221, by = c("hhgrap", "hhnum")) 
outtrans231 <- outtrans23 %>%
  group_by(hhgrap, hhnum) %>%
  summarize(
    sum1_outtrans = sum(as.numeric(q13_39a), na.rm = TRUE),
    sum2_outtrans = sum(as.numeric(q13_42a), na.rm = TRUE)
  ) %>%
  ungroup()
outtrans231 <- outtrans231 %>%
  mutate(sum_outtrans = as.numeric(sum1_outtrans) + as.numeric(sum2_outtrans))
outtrans232 <- outtrans23 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(outtrans231, by = c("hhgrap", "hhnum")) 
```

```{r}
#create year variable
outtrans202$year <- 2020
outtrans212$year <- 2021
outtrans222$year <- 2022
outtrans232$year <- 2023
```

```{r}
outtrans <- bind_rows(outtrans202, outtrans212, outtrans222, outtrans232)
```

```{r}
outtrans <- outtrans %>%
  distinct(hhgrap, hhnum, year, .keep_all = TRUE)
df <- left_join(df, outtrans, by = c("hhgrap", "hhnum","year"))
```

mechanism on asset
```{r}
asset20 <- read_dta("raw_data/HPS2020/S12_AVOI.dta")
asset21 <- read_dta("raw_data/HPS2021/S12_AVOI.dta")
asset22 <- read_dta("raw_data/HPS2022/S12_AVOI.dta")
asset23 <- read_dta("raw_data/HPS2023/S12_AVOI.dta")
```

```{r, include=FALSE, echo=FALSE}
asset201 <- asset20 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_asset = sum(as.numeric(q12_032), na.rm = TRUE), 
  ) %>%
  ungroup() 
asset202 <- asset20 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(asset201, by = c("hhgrap", "hhnum")) 
asset211 <- asset21 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_asset = sum(as.numeric(q12_032), na.rm = TRUE), 
  ) %>%
  ungroup() 
asset212 <- asset21 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(asset211, by = c("hhgrap", "hhnum")) 
asset221 <- asset22 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_asset = sum(as.numeric(q12_032), na.rm = TRUE), 
  ) %>%
  ungroup() 
asset222 <- asset22 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(asset221, by = c("hhgrap", "hhnum")) 
asset231 <- asset23 %>%
  group_by(hhgrap, hhnum) %>%  
  summarize(
    sum_asset = sum(as.numeric(q12_032), na.rm = TRUE), 
  ) %>%
  ungroup() 
asset232 <- asset23 %>%
  distinct(hhgrap, hhnum, .keep_all = TRUE) %>% 
  left_join(asset231, by = c("hhgrap", "hhnum")) 
```

```{r}
#create year variable
asset202$year <- 2020
asset212$year <- 2021
asset222$year <- 2022
asset232$year <- 2023
```


```{r}
asset <- bind_rows(asset202, asset212, asset222, asset232)
```

```{r}
asset <- asset %>%
  distinct(hhgrap, hhnum, year, .keep_all = TRUE)
df <- left_join(df, asset, by = c("hhgrap", "hhnum","year"))
```

```{r}
write_dta(df, "food_cyclone.dta")
```

